### 2008-09-09 doc/client/arc-ws-clients.tex
Rename ap clients to arc clients and remove asstat??

\section{Job Submission}
\label{sec:apsub}

The \verb#apsub# command is used to submit jobs to an A-REX service.

\begin{shaded}
\paragraph{Usage} \verb:apsub <JSDL-file> <JobID-file>:
\end{shaded}

@@

\section{Job Status Query}
\label{sec:apstat}

The \verb#apstat# command is used to query the status of a job that
has been submitted to an A-REX service.

\begin{shaded}
\paragraph{Usage} \verb:apstat <JobID-file>:
\end{shaded}

\paragraph{Arguments}
\begin{description}
\item[\texttt{<JobID-file>}] The name of a file in which the
Job ID is stored. This file was created by \verb:apsub: when the job
was submitted.
\end{description}

@@

\section{Job Termination}
\label{sec:apkill}

The \verb#apkill# command is used to terminate a job that has been
submitted to an A-REX service.

\begin{shaded}
\paragraph{Usage} \verb:apkill <JobID-file>:
\end{shaded}

\paragraph{Arguments}
\begin{description}
\item[\texttt{<JobID-file>}] The name of a file in which the
Job ID is stored. This file was created by \verb:apsub: when the job
was submitted.
\end{description}

>>>>

\section{Job Submission}
\label{sec:arcsub}

The \verb#arcsub# command is used to submit jobs to an A-REX service.

\begin{shaded}
\paragraph{Usage} \verb:arcsub <JSDL-file> <JobID-file>:
\end{shaded}

@@

\section{Job Status Query}
\label{sec:arcstat}

The \verb#arcstat# command is used to query the status of a job that
has been submitted to an A-REX service.

\begin{shaded}
\paragraph{Usage} \verb:arcstat <JobID-file>:
\end{shaded}

\paragraph{Arguments}
\begin{description}
\item[\texttt{<JobID-file>}] The name of a file in which the
Job ID is stored. This file was created by \verb:arcsub: when the job
was submitted.
\end{description}

@@

\section{Job Termination}
\label{sec:arckill}

The \verb#arckill# command is used to terminate a job that has been
submitted to an A-REX service.

\begin{shaded}
\paragraph{Usage} \verb:arckill <JobID-file>:
\end{shaded}

\paragraph{Arguments}
\begin{description}
\item[\texttt{<JobID-file>}] The name of a file in which the
Job ID is stored. This file was created by \verb:arcsub: when the job
was submitted.
\end{description}

### 2008-09-09 doc/ws-quick-guide/ws-quick-guide.tex
Rename apecho -> arcecho
Rename ap clients to arc clients and remove asstat??

\begin{lstlisting}
$ARC_LOCATION/bin/apecho <message>
\end{lstlisting}

@@

A-REX accepts jobs described in JSDL language. Example JSDL jobs are provided in
\verb|$ARC_LOCATION/share/doc/| in files \verb|jsdl_simple.xml| and
\verb|jsdl_stage.xml|. To submit job to A-REX service one may use
\texttt{apsub} command:

\begin{lstlisting}
$ARC_LOCATION/bin/apsub https://localhost:60000/arex
 /usr/local/share/doc/arc/jsdl_simple.xml id.xml
\end{lstlisting}

If everything goes properly somewhere in it's output there should be a message
``Submitted the job!''. Obtained job identifier is an XML document and is stored
in id.xml file. It may then be used to query job state with \texttt{apstat}
utility:

\begin{lstlisting}
$ARC_LOCATION/bin/apstat id.xml 2>/dev/null
Job status: Running/Submiting

$ARC_LOCATION/bin/apstat id.xml 2>/dev/null
Job status: Running/Finishing

$ARC_LOCATION/bin/apstat id.xml 2>/dev/null
Job status: Finished/Finished
\end{lstlisting}

Full set of A-REX client tools consists of \texttt{apsub}, \texttt{apstat},
\texttt{apkill}, \texttt{asstat}, \texttt{apget} and \texttt{apclean} commands.
For more information please see man pages ot those utilities.

>>>>

\begin{lstlisting}
$ARC_LOCATION/bin/arcecho <message>
\end{lstlisting}

@@

A-REX accepts jobs described in JSDL language. Example JSDL jobs are provided in
\verb|$ARC_LOCATION/share/doc/| in files \verb|jsdl_simple.xml| and
\verb|jsdl_stage.xml|. To submit job to A-REX service one may use
\texttt{arcsub} command:

\begin{lstlisting}
$ARC_LOCATION/bin/arcsub https://localhost:60000/arex
 /usr/local/share/doc/arc/jsdl_simple.xml id.xml
\end{lstlisting}

If everything goes properly somewhere in it's output there should be a message
``Submitted the job!''. Obtained job identifier is an XML document and is stored
in id.xml file. It may then be used to query job state with \texttt{arcstat}
utility:

\begin{lstlisting}
$ARC_LOCATION/bin/arcstat id.xml 2>/dev/null
Job status: Running/Submiting

$ARC_LOCATION/bin/arcstat id.xml 2>/dev/null
Job status: Running/Finishing

$ARC_LOCATION/bin/arcstat id.xml 2>/dev/null
Job status: Finished/Finished
\end{lstlisting}

Full set of A-REX client tools consists of \texttt{arcsub}, \texttt{arcstat},
\texttt{arckill}, \texttt{arcget} and \texttt{arcclean} commands.
For more information please see man pages ot those utilities.
